---
title: | 
  Advanced statistics and Open science
format:
  html:
    toc: true
    css: ../css/header.css
execute: 
  freeze: false
---

{{< include ../_links.qmd >}}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

This is the site for the graduate level course Bio8940  at the University of Ottawa.
You will find all the course information including the course schedule, slides, course notes, practicals info and exercises, description of assessments as well as the (official)  for the course.

Submission of course work is done via [brighspace](https://uottawa.brightspace.com/d2l/home).


Please note that the class is bilingual. This means that any questions during the class can be asked or answered in either french or english and the prof will translate the answers if needs be. The majority of the course content (slides and course notes) are provided in english only, but explanation can be provided in either languages.

{{< include who_when.qmd >}}

# Open science resources

I developed proposal and thesis templates that are 1. useable directly as Quarto a extension, 2. provide brief explanation of the expected content of each section, and 3. generate pdf documents appropriately formatted for uOttawa requirements (at least biology)

* [bio-uo-proposal](https://github.com/JulienGAMartin/quarto-bio-uo-proposal) quarto extension providing 1 new pdf output format (`bio-uo-proposal-pdf`). I am working on a docx version but tweaking the frontpage is tricky with word document. 

* [bio-uo-thesis](https://github.com/JulienGAMartin/quarto-bio-uo-thesis): quarto extension  providing two new output formats for book projects: an html (`bio-uo-thesis-html`) and a pdf (`bio-uo-thesis-pdf`) generating a website (to be hosted on github pages or similar) and a pdf of the thesis adequately formatted for uOttawa (at least biology)

* [bio-uo-stat](https://github.com/JulienGAMartin/bio-uo-stat): quarto extension to render your Bio8940 final report as a nicely formatted PDF

# Software and account requirements

<!-- * Download and install [Git](https://git-scm.com/downloads). -->

* a GitHub account. (Set up a free account [here](https://github.com/)).

* [`R`][cran] and your favourite R IDE [`RStudio`][rstudio_d] or [`VSCode`][vscode_d]

* [`git`][git_install] software

* [`quarto`][quarto_install] software

<!-- * Have Git, GitHub and RStudio talk to each other following [these guidelines (section 2.2.2 Configuration only)](https://inbo.github.io/git-course/course_rstudio.html#222_configuration). -->

<!-- * Install the following `R` packages: `tidyverse`, `sf`, `emo`, `janitor`, `palmerpenguins`, `usethis` and `lubridate.` You can install them all at once by running the following code in the `R` command line: -->

```{r eval = FALSE, echo = FALSE}
install.packages(c("tidyverse", "sf", "emoji", "janitor", "palmerpenguins", "usethis", "lubridate"))
```

--------------------------------------------------------------------------------


#### Reuse {-}

Text and figures are licensed under Creative Commons Attribution [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/). Any computer code (R, HTML, CSS, etc.) in slides and worksheets, including in slide and worksheet sources, is also licensed under [MIT](https://github.com/biostats-uOttawa/bio8940/blob/master/LICENSE.md). 

