---
title: Lectures
execute: 
  freeze: false
---

{{< include ../_links.qmd >}}

```{r}
#| echo: false
#| include: false
knitr::opts_chunk$set(echo = FALSE)
library(gt)
library(tidyr)
library(lubridate)
source("../_yaml_extract.R")
dat <- read_yaml("../_course.yml")
extract_course(dat)
```


# Schedule 

```{r}
check <- character(0)
schedule <- schedule_df %>%
  rowwise() %>%
  mutate(
    qmd_file = ifelse(
      identical(
        str_subset(
          list.files("../slides", pattern = "qmd", full.names = TRUE),
          pattern = sprintf("lec-%.2d", week)
        ),
        check
      ),
      NA,
      str_subset(
        list.files("../slides", pattern = "qmd", full.names = TRUE),
        pattern = sprintf("lec-%.2d", week)
      )
    ),
    lecture_file = ifelse(!is.na(qmd_file),
      gsub("qmd", "slides.html", qmd_file),
      NA
    ),
    notes_file = ifelse(!is.na(qmd_file),
      gsub("qmd", "notes.html", qmd_file),
      NA
    ), ,
    lecture = !is.na(lecture_file)
  ) %>%
  ungroup() %>%
  arrange(week) %>%
  mutate(
    Slides = case_when(
     lecture == TRUE ~ glue("<a class='fa fa-display' href='{lecture_file}' target='_blank'></a> <a class='fa fa-note-sticky' href='{notes_file}' target='_blank'></a>"),
     TRUE ~ NA_character_
    ),
    Topic = topic,
    #    Assessment = ifelse(is.na(assessment), " ", assessment),
    Reading = reading,
    Date =  as.Date(ifelse(
     (ymd(dat$date_start) + weeks(week - 1)) > ymd(dat$date_read),
     ymd(dat$date_start) + weeks(week),
     ymd(dat$date_start) + weeks(week - 1)
     ))
  ) %>%
  replace_na(list(Topic = "",  Reading = "none")) %>%

  select(Date, Topic, Slides, Reading) # , Assessment)
```

```{r}
midsem_break <- sum(schedule$Date < ymd(dat$date_read))

schedule %>%
  gt() |>
  #  cols_label(week = "Week") |>
  fmt_markdown(columns = c("Slides", "Reading")) |>
  fmt_date(
    columns = Date,
    date_style = "MMMd",
    locale = "en"
  ) |>
  tab_row_group(
    label = "Reading week",
    rows = (midsem_break + 1):12
  ) |>
  row_group_order(groups = c(NA, "Reading week")) |>
  cols_width(
    Date ~ px(50),
    Slides ~ px(20)
  )
```

## About slides {{< fa display >}} and notes {{< fa note-sticky >}}

### Slides {{< fa display >}} 

Slides in `revealjs` format (html). If you want then as a pdf (*note you might loose some functionality or contents due to tabs and scroll sections*):

1. Open the slides in your browser from a link on this page
2. Press `e` to get into the PDF export mode (*`?print-pdf` should appear near the end of the url and white borders should appear*)
1. Open the in-browser print dialog (CTRL/CMD+P).
1. Change the `Destination` setting to `Save as PDF`.
1. Change the `Layout` to `Landscape`.
1. Change the `Margins` to `None`.
1. Enable the Background graphics option (if you want it)
1. Click Save 🎉

### Notes {{< fa note-sticky >}}

Content of the slides in html format as a self-contained downloadable file and including tabs and scroll sections. 

More importantly, notes have the commenting and annotateing tools activated via <https://hypothes.is/>. If you create a free account , you can annotate and comment slides as well as share your annotations/comments with the public or via private or public groups.
